---
title: "Homework 5"
output: github_document
---

```{r setup, message = FALSE}
library(tidyverse)


knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
```{r}
# Load dataset
homicide = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state), 
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved", 
      disposition == "Open/No arrest" ~ "unsolved", 
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

```{r}
# the total number of homicides
homicide %>% 
  count(city_state)

# the number of unsolved homicides
homicide %>%  
  filter(resolution == "unsolved") %>% 
  count(city_state)
```

Focus on Baltimore, MD

```{r}
baltimore_df = 
  homicide %>% 
  filter(city_state == "BaltimoreMD")

# estimate the proportion of homicides that are unsolved
baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>%  pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

Iterate across cities

```{r}
# write a function
prop_test_function = function(city_df){
  city_summary = 
  city_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  )

city_test = 
  prop.test(
  x = city_summary %>% pull(unsolved), 
  n = city_summary %>%  pull(n)
)
  return(city_test)
}

```

```{r}
# iterate the pro_test_function across cities by nesting dataframes together
results_df = 
  homicide %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
    geom_point() +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    labs(
      title = "Estimates and CIs for each City", 
      x = "City and State", 
      y = "Estimate"
    )
```

## Problem 2
#### Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
```{r, message = FALSE}
longitudinal = tibble(
  files = list.files("./data/problem2_data/")) %>% 
  mutate(data = map(.x = files, ~ read_csv(paste0("./data/problem2_data/", .x)))) %>% 
  unnest(cols = data) %>% 
  separate(files, into = c("arm", "subject_id"), sep = "\\_") %>% 
  mutate(
    subject_id = str_replace(subject_id, "\\.csv", ""), 
    subject_id = str_c(arm, subject_id, sep = "_"),
    arm = ifelse(arm == "con", "control", "experimental")) %>% 
  select(subject_id, everything())

knitr::kable(longitudinal)
```

#### Make a spaghetti plot showing observations on each subject over time: 

```{r}
plot = 
  longitudinal %>% 
  pivot_longer(
    cols = week_1:week_8,
    names_to = "time",
    values_to = "data"
  )

plot %>% 
  ggplot(aes(x = time, y = data, group = subject_id, color = arm)) +
  geom_point(size = 0.7) +
  geom_line() +
  labs(
    title = "Observations on Each Subject over Time", 
    x = "Time (weeks)", 
    y = "Observation"
  )
```

On week one, the observations from the control arm and experimental arm do not show significant differences. Over time, the observations from the control arm tend to be more stable, while the observations from the experimental arm are steadily increasing. On week eight, all subjects in the experimental arm have higher values of observations than all subjects in the control arm. 

## Problem 3

Loads the iris dataset: 
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

#### Write a function to fill in missing values

```{r}
fill_in_missing = function(x){
  if(is.numeric(x)){
    replace(x, is.na(x), mean(x, na.rm = TRUE))
  }
  
  else if(is.character(x)){
    replace(x, is.na(x), "virginica")
  }
}

filled_iris = 
  iris_with_missing %>% 
  map_df(fill_in_missing) 
```

